The goal of this project was to demonstrate our capacity to analyse, create, and implement current C/C++ code to add new features. The SLD2 library was included in the skeleton code for the basic game which we had to utilize to run the graphical components of the game. The Theme I used throughout was a moon-based space game. Making the player in this case a human astronaut. The main objective for the player in this game is to collect all the neon blue orbs on each map. The player will have to navigate across the maps using platforms and blocks and will have to avoid taking damage from the aliens.

I have implemented about five features, four new maps and have created twenty-two textures. The features that I have implemented were the ability for the player to choose to do a different map or level. Additionally, a menu screen is displayed at the start of the game to allow the user to choose one of the five maps/levels made available to them. Moving Aliens that decrees the players health or kills the player when the character interacts with it was also implemented and the player was given the ability to shoot when the ‘shift’ button was held, this allowed the player to kill the Alien. In addition to functional change, I have also changed the texture of the blocks, character, background, and platform to fit the theme of the game.

The Programming style used by me is mainly imperative as C was predominately used to implement all the new features. Although for components such as entities structs were used to store objects such as enemies and player information so it can be more accessible to other functions. The public functions in the skeleton code and some of the ones I implemented were stored in the commons.h file. 

In this report, I will go through the development decisions and design choices I made for these features I implemented. This report will consist of four additional components. In design I will be focusing on the UI and textures and the objects and its features. In the implementation and development section I will go into more detail about each feature and describe the development process of each feature more clearly, additionally, I will Justify my changes compared to keeping the original design. And finally, describe improvements or alternative features I could have used in the conclusions. The difference of code will also be available at the end of this document, comparing the original skeleton code provided to the code that I wrote.
